---
title: "Visualization with ggplot2"
author: "By: Anjali Gautam"
output: rmarkdown::github_document
---

Below are codes to create basic visualizations in R package ggplot2. This is for someone who wants to start with ggplot2 or use it for basic purposes. I will use R datasets to create these visualizations and will update the code as new visualizations are discovered 

```{r message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_figs/README-"
)
```

```{r warning=FALSE}
library(ggplot2)
```

#### Histogram

R data "cars" will be used for this plot

```{r}
data("cars")
str(cars)
```

```{r}
ggplot(cars,aes(speed))+
  geom_histogram(binwidth = 1, fill="lightblue", color = "blue")+
  labs(x="Speed", y = "Count of cars/Frequency")+
  ggtitle("Histogram")
```

#### Line chart 

R data "phones" will be used for this plot

```{r}
data("phones")
head(phones)
```

I will plot weight of chicks with time 

```{r}
ggplot(data= as.data.frame(phones), aes(x=year, y = calls))+
  geom_line(color="grey")+
  geom_point(color="black")+
  labs(y="no of calls")+
  ggtitle("Line Chart")
```

